Summary of Possibilities

### 2018-06-24 k-Means Miriam/PCA.tex
miriams part

\section{Clustering with RapidMiner}

RapidMiner has different Modules for Clustering already implemented. We apply the k-Means algorithm with mixed measure (euclidean).

\includegraphics[width=0.9\textwidth]{ClusteringRapid.PNG}

@@

\subsection{Original Data}

Applying this process to the original data you can see without alignment of strata and cluster, that the distribution of cluster and strata is not close to the same.

\ref{fig:OrgDist}. 
\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.4\linewidth]{ClusterPCAOrigRapidStrata.PNG}
  \caption{Strata}
  \label{fig:OrgSt}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.4\linewidth]{ClusterPCAOrigRapidCluster.PNG}
  \caption{Cluster}
  \label{fig:OrgCl}
\end{subfigure}
\caption{Distribution of original data}
\label{fig:OrgDist}
\end{figure}

>>>>

\section{PCA}

\textbf{PCA} uses an orthogonal transformation (vectors multiplied are 0) to
convert a dataset with maybe correlated datas into a dataset withou
correlations.

Rapidminer has a tool applying the PCA algorithm on given data. Output are the
new attributes, which are a combination of the old ones.

\subsection{Rapidminer Process}
\includegraphics[width=0.9\textwidth]{PCAClustering}

@@

This is the basis for all datasets.

\subsection{Applying on original data}
Applying the PCA module on the original data without EST and a variance
threshold of 0.95 we get two Attributes, so we can assume, that the data is strongly connected. As expected the computating time decreases a lot.

For a clustering of 6 clusters we get a distribution that is complete different from the original distribution \ref{fig:OrgDist}. 
\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.4\linewidth]{ClusterOrigRapidStrata.PNG}
  \caption{Strata}
  \label{fig:OrgSt}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.4\linewidth]{ClusterOrigRapidCluster.PNG}
  \caption{Cluster}
  \label{fig:OrgCl}
\end{subfigure}
\caption{Distribution of original data}
\label{fig:OrgDist}
\end{figure}
